An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-01-13 paper.tex
Spelling.

The MATLAB script and Simulink model produce a comma-delimited text file of
five desired belt speed signals indexed by the time stamp. There are slow, normal,
and fast walking speeds and slow and fast running speeds.~\footnote{The running
signals were not used in the experiments presented in this paper.} The measured
speed of the treadmill belts from unloaded trials (79, 80, 81) are compared to
these commanded treadmill control input signals in
Figure~\ref{fig:input_output} to show the effect of the treadmill and
controller dynamics. The system introduces a delay and seems to act as a low
pass filter. The standard deviations of the measured speeds do not
significantly differ from the desired values:
\SIlist{0.05;0.12;0.2}{\meter\per\second} for the three speeds, respectively.
%
\begin{figure}
  \centering
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Treadmill belt speed input signals (purple) and recorded output
    speeds (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively.}
  \label{fig:input_output}
\end{figure}

>>>>

The MATLAB script and Simulink model produce a comma-delimited text file of
five desired belt speed signals indexed by the time stamp. There are slow, normal,
and fast walking speeds and slow and fast running speeds.~\footnote{The running
signals were not used in the experiments presented in this paper.} The measured
speed of the treadmill belts from unloaded trials (79, 80, 81) are compared to
the commanded treadmill control input signals in
Figure~\ref{fig:input_output} to show the effect of the treadmill and
controller dynamics. The system introduces a delay and seems to act as a low
pass filter. The standard deviations of the measured speeds do not
significantly differ from the desired values:
\SIlist{0.05;0.12;0.2}{\meter\per\second} for the three speeds, respectively.
%
\begin{figure}
  \centering
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Treadmill belt speed input signals (purple) and recorded output
    speeds (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively.}
  \label{fig:input_output}
\end{figure}
